### 2016-08-31 version0.0/asli.tex
Applying R.A's comments on the ch3.
Applying part of Sarah's comments on ch4
Adding an appendix about Bayesian fitting
correct typos in CV

{\bf Chapter 3}: Data Mining in Nearby Galaxies, will be submitted in the near future. %TBD: change this if you change the title

@@

\newcommand \kpc        {\,{\rm kpc}}
\newcommand \sigmagas    {$\Sigma_{\mathrm{gas }} $\ }
\newcommand \sigmatotalgas {$\Sigma_{\mathrm {total\, gas }} $\ }
\newcommand{\eqsigmagas}    {\Sigma_{\mathrm {gas }}}
\newcommand{\sigmasfr}   {$\Sigma_{\mathrm {sfr }} $\ }
\newcommand{\eqsigmasfr}{\Sigma_{\mathrm{sfr }}}
\newcommand{\sigmastar}    {$\Sigma_{\mathrm {star }} $\ }
\newcommand{\eqsigmastar}    {\Sigma_{\mathrm {star }}}
\newcommand{\halpha}    {H$\alpha\ $}
\newcommand{\um}    {$\mu$m\ }
\newcommand{\mice} {$\mu$m}
\newcommand{\nprime}{N$^\prime$}
\newcommand \boldit {\textbf{\textit{}}}
\newcommand{\eqnprime} {N^\prime}
\newcommand{\degr} {$^{\circ}$}
\newcommand{\arcmin} {$^{\prime}$}
\newcommand {\arcsec} {$^{\prime\prime}$}
\newcommand \Spitzer {{\it Spitzer }}
\newcommand \Galex {GALEX\ }
\newcommand \GALEX {GALEX\ }
\newcommand \Herschel {{\it Herschel }}
\newcommand \sii {[S~\textsc{ii}]} 
\newcommand \oiii {[O~\textsc{iii}]} 
\newcommand \hi {H~\textsc{i}}
\newcommand \hii {H~\textsc{ii}}
\newcommand \oii {[O~\textsc{ii}]}
\newcommand \nii {[N~\textsc{ii}]}

@@

% %Appendices.
 \begin{appendices}
 \include{appendixa}
 \include{appendixa_2}
 \include{appendixb}
\include{appendixc}
 \end{appendices}

%CV only relevant stuff... not full CV.
 \addcontentsline{toc}{chapter}{Curriculum Vitae}
\chapter*{Curriculum Vitae}
\begin{table}[ht]
\begin{tabular}{ll}
\textbf{Name:} & \firstname{} \lastname\\\\
\textbf{Post-Secondary} & {\sl Doctor of Philosophy,} Astronomy \\
\textbf{Education and}& Western University\\
\textbf{Degrees:}& London, ON\\
& 2012 - 2016\\\\
&{\sl Master of Science,} Astronomy \\
& University of Sussex \\
& Brighton, England\\
& 2011 - 2012\\\\
& {\sl Bachelor of Science,} Physics \\
& Sharif University of Technology \\
& Tehran, Iran \\
& 2006 - 2011\\\\
\textbf{Honours and}& {\sl Western University Graduate Research Scholarship}\\
\textbf{Awards:}&(2012-2016)\\\\
& {\sl Travel Grant for Statistical Challenges in Modern Astronomy VI,}\\
&  Pittsburgh, PA (Spring, 2016)\\\\
% &{\sl Travel Grant for Canadian Astronomical Society Conference (CASCA),} \\
% & Winnipeg, MB (Spring, 2016)\\
&{\sl Scholarship for Utrecht Summer School on Star formation,}\\
&Utrecht, Netherlands (Summer, 2009)\\\\
\textbf{Related Work}& Graduate Research \& Teaching Assistant\\
\textbf{Experience:}& Western University\\
& 2012 - 2016\\\\
% & Instructor for Software Carpentry\\
% & 2015 - 2016\\\\
&Graduate Research Assistant\\
& University of Sussex \\
& 2011 - 2012\\\\
\end{tabular}
\end{table}

\subsubsection*{Publications:}
 \textbf{Rahmani. S}, Lianou. S, Barmby. P, ``{\em Star formation laws in the Andromeda galaxy: gas, stars, metals and the surface density of star formation}'', 2016, MNRAS, 456, 4128\\
\textbf{Rahmani. S}, Teimoorinia. H, Barmby. P, `` {\em Classifying galaxy spectra at $0.5<z<1$: an unsupervised approach}", Submitted to MNRAS, JUNE,2016\\

\subsubsection*{Work in Preparation}
 \textbf{Rahmani. S}, Teimoorinia. H, Peeters. E, Barmby. P, `` {\em Data Mining in nearby galaxies}", In prep.\\

\subsubsection*{Conferences Talks}

@@

{\sl International Tusi Conference on Astrophysics, devoted to the Maragha Observatory's 750th year
anniversary, Maragha, Iran} \hfill(2009)
\begin{itemize} 
\item Rahmani, S., Mashhoon, M., Moghaddam , A., ``Challenges of brightness variations of Planets: From Geocentric to Heliocentric" 
\end{itemize}
\subsubsection*{Conferences Posters}
{\sl Statistical challenges in Modern Astronomy {\textsc VI}, Pittsburgh, PA}\hfill(2016)
\begin{itemize} 
\item Rahmani, S., Teimoorinia, H., Peeters, E.,  Barmby, P. 2013, ``Data mining in nearby galaxies" 
\end{itemize}

{\sl From galactic to extra galactic star formation (GESF), Marsseile, France}\hfill (2014)
\begin{itemize} 
\item Rahmani, S., Barmby, P. 2013, ``Which Star formation laws in M31?" 
\end{itemize}

{\sl Canadian Astronomical Society Conference (CASCA), University of British Colombia, BC}\hfill (2013)
\begin{itemize} 
\item Rahmani, S., Barmby, P. 2013, ``Effects of Gas Clouds and Existing Stars on Current Star Formation in M31: Testing the Extended Schmidt Law" 
\end{itemize}

>>>>

{\bf Chapter 3}: Data Mining in Nearby Galaxies, will be submitted in the near future.

@@

\newcommand \kpc        {\,{\rm kpc}}
\newcommand \sigmagas    {$\Sigma_{\mathrm{gas }} $\ }
\newcommand \sigmatotalgas {$\Sigma_{\mathrm {total\, gas }} $\ }
\newcommand{\eqsigmagas}    {\Sigma_{\mathrm {gas }}}
\newcommand{\sigmasfr}   {$\Sigma_{\mathrm {sfr }} $\ }
\newcommand{\eqsigmasfr}{\Sigma_{\mathrm{sfr }}}
\newcommand{\sigmastar}    {$\Sigma_{\mathrm {star }} $\ }
\newcommand{\eqsigmastar}    {\Sigma_{\mathrm {star }}}
\newcommand{\halpha}    {H$\alpha\ $}
\newcommand{\halphadot}    {H$\alpha$}
\newcommand{\um}    {$\mu$m\ }
\newcommand{\mice} {$\mu$m}
\newcommand{\nprime}{N$^\prime$}
\newcommand \boldit {\textbf{\textit{}}}
\newcommand{\eqnprime} {N^\prime}
\newcommand{\degr} {$^{\circ}$}
\newcommand{\arcmin} {$^{\prime}$}
\newcommand {\arcsec} {$^{\prime\prime}$}
\newcommand \Spitzer {{\it Spitzer }}
\newcommand \Galex {GALEX\ }
\newcommand \GALEX {GALEX\ }
\newcommand \Herschel {{\it Herschel }}
\newcommand \sii {[S~\textsc{ii}]} 
\newcommand \oiii {[O~\textsc{iii}]} 
\newcommand \hi {H~\textsc{i}}
\newcommand \hii {H~\textsc{ii}}
\newcommand \oii {[O~\textsc{ii}]}
\newcommand \nii {[N~\textsc{ii}]}

@@

% %Appendices.
 \begin{appendices}
 \include{appendixa}
 \include{appendixa_2}
 \include{appendixa_3}
 \include{appendixb}
\include{appendixc}
 \end{appendices}

%CV only relevant stuff... not full CV.
 \addcontentsline{toc}{chapter}{Curriculum Vitae}
\chapter*{Curriculum Vitae}
\begin{table}[ht]
\begin{tabular}{ll}
\textbf{Name:} & \firstname{} \lastname\\\\
\textbf{Post-Secondary} & {\sl Doctor of Philosophy,} Astronomy \\
\textbf{Education and}& Western University\\
\textbf{Degrees:}& London, ON\\
& 2012 - 2016\\\\
&{\sl Master of Science,} Astronomy \\
& University of Sussex \\
& Brighton, England\\
& 2011 - 2012\\\\
& {\sl Bachelor of Science,} Physics \\
& Sharif University of Technology \\
& Tehran, Iran \\
& 2006 - 2011\\\\
\textbf{Honours and}& {\sl Western University Graduate Research Scholarship}\\
\textbf{Awards:}&(2012-2016)\\\\
& {\sl Travel Grant for Statistical Challenges in Modern Astronomy VI,}\\
&  Pittsburgh, PA (Spring, 2016)\\\\
% &{\sl Travel Grant for Canadian Astronomical Society Conference (CASCA),} \\
% & Winnipeg, MB (Spring, 2016)\\
&{\sl Scholarship for Utrecht Summer School on Star Formation,}\\
&Utrecht, Netherlands (Summer, 2009)\\\\
\textbf{Related Work}& Graduate Research \& Teaching Assistant\\
\textbf{Experience:}& Western University\\
& 2012 - 2016\\\\
% & Instructor for Software Carpentry\\
% & 2015 - 2016\\\\
&Graduate Research Assistant\\
& University of Sussex \\
& 2011 - 2012\\\\
\end{tabular}
\end{table}

\subsubsection*{Publications:}
 \textbf{Rahmani, S.}, Lianou, S., Barmby, P., ``{\em Star formation laws in the Andromeda galaxy: gas, stars, metals and the surface density of star formation}'', 2016, MNRAS, 456, 4128\\
\textbf{Rahmani, S.}, Teimoorinia, H., Barmby, P., `` {\em Classifying galaxy spectra at $0.5<z<1$: an unsupervised approach}", Submitted to MNRAS, June ,2016\\

\subsubsection*{Work in Preparation}
 \textbf{Rahmani, S.}, Teimoorinia, H., Peeters, E., Barmby, P., `` {\em Data Mining in nearby galaxies}", in prep.\\

\subsubsection*{Conference Talks}

@@

{\sl International Tusi Conference on Astrophysics, devoted to the Maragha Observatory's 750th year
Anniversary, Maragha, Iran} \hfill(2009)
\begin{itemize} 
\item Rahmani, S., Mashhoon, M., Moghaddam, A., ``Challenges of brightness variations of Planets: From Geocentric to Heliocentric" 
\end{itemize}
\subsubsection*{Conference Posters}
{\sl Statistical Challenges in Modern Astronomy {\textsc VI}, Pittsburgh, PA}\hfill(2016)
\begin{itemize} 
\item Rahmani, S., Teimoorinia, H., Peeters, E.,  Barmby, P. 2013, ``Data mining in nearby galaxies" 
\end{itemize}

{\sl From galactic to extra galactic star formation (GESF), Marsseile, France}\hfill (2014)
\begin{itemize} 
\item Rahmani, S., Barmby, P. 2013, ``Which Star Formation Laws in M31?" 
\end{itemize}

{\sl Canadian Astronomical Society Conference (CASCA), Vancouver, BC}\hfill (2013)
\begin{itemize} 
\item Rahmani, S., Barmby, P. 2013, ``Effects of Gas Clouds and Existing Stars on Current Star Formation in M31: Testing the Extended Schmidt Law" 
\end{itemize}
